---
title: "index"
output: html_document
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
require(dplyr)

#reads in chart 1 file
source("c:/info498f/homework/a7-collaborative-coding/scripts/chart1.r")

#reads in chart 2 file
source("c:/info498f/homework/a7-collaborative-coding/scripts/chart2.r")

#reads in the summary file
source("c:/info498f/homework/a7-collaborative-coding/scripts/summary.r")

#reads in the survey data
data <- read.csv("https://raw.githubusercontent.com/INFO-498F/a7-survey-data/master/intro_survey_data.csv")

data <- rename(data, class = What.is.your.current.class.standing.)
data <- rename(data, interested_in_info = Are.you.interested.in.applying.to.the.Informatics.major.)
data <- rename(data, operating_system = What.operating.system.do.you.typically.use.)

data_info <- info_function(data)
```

The survey taken at the beginning of the class asked `r data_info[1]` questions of `r data_info[2]` students. These questions revealed that the average number of countries visited by students was `r data_info[3]`. Out of the `r data_info[2]` students, `r data_info[4]` of them use macs and `r data_info[5]` use windows based machines. Chart 1 shows the distribution of different class standings in the class. Chart 2 shows the average experience in various different parts of the class across the different operating systems.

```{r, echo=FALSE} 
#renders charts 1 and 2
chart1(data)
chart2(data)
```